\documentclass[10pt]{article}

% Preamble

\usepackage{amsmath,amsfonts,amssymb}
\usepackage[mathscr]{euscript}
%\usepackage[mathcal]{euscript}
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage{float}
\usepackage{bbm}
\usepackage{braket}
\usepackage{tikz-feynman}
\usepackage{simpler-wick}
\usepackage{cancel}
\usepackage{stackengine}
\usepackage{slashed}
\usepackage{caption}
\usepackage{pgfplots}

\newcommand{\bigzero}{\mbox{\normalfont\Large\bfseries 0}}

\title{Notes On Introduction to Conformal Field Theory \\ A Course Given By Dr. Tobias Osborne}
\author{Transcribed by Dr. Alexander V. St. John}

% The Document

\begin{document}

\maketitle

\clearpage

\section*{Lecture 1: Introduction to Conformal Field Theory}
\label{sec: lec1}

\noindent Recommended references:

\begin{itemize}
\item \textit{A Mathematical Introduction to Conformal Field Theory} by Schottenloher.
\item \textit{Applied Conformal Field Theory}, hep-th/9108028, by Ginsparg.
\item \textit{Conformal Field Theory} (``Yellow Book'') by Francesco, Mathieu, Senechal.
\end{itemize}

\noindent Why study conformal field theory (CFT)?

\begin{itemize}
\item CFT provides a good description of systems at or near criticality.
\item CFTs are the only true quantum field theories (QFTs), since they are cutoff-independent. One can think of QFTs as perturbations of CFTs. CFTs correspond to renormalization groups of fixed points, which dominate an effective theory at or near criticality.
\item CFTs can be made, by and large, mathematically rigorous, at least in $(1+1)$-dimensional theories. There are three major competing mathematical descriptions for CFT, and advances are being made towards a single, unifying description.
\end{itemize}

\noindent Prerequisites for this material:

\begin{itemize}
\item Advanced quantum mechanics
	\subitem E.g, many-body theory and Fock spaces.
\item Classical field theory
	\subitem E.g., symplectic geometry.
\item Quantum field theory.
\item Advanced quantum field theory.
\end{itemize}

\noindent What is CFT?

\begin{itemize}
\item A \textit{conformal field theory} is a field theory, quantum or classical, that is invariant, or symmetric, under a group of transformations called the \textit{conformal group} $G$.
\item In a classical field theory, this means that the equations of motion are left invariant.
\item In a quantum field theory, this means that, by Wigner's theorem, there is a projective unitary representation of the group $G$. In other words, symmetries, or transformations, that leave the transition amplitude invariant, are realized, up to a phase, by (anti)unitary operators.
\end{itemize}

\subsection*{Conformal Transformations in $d$ Dimensions}

\noindent Let $M = \mathbb{R}^{p,q}$ be a manifold $\mathbb{R}^d$, where $d = p+q$, and $p,q \in \mathbb{Z}_{\ge 0}$. To this manifold, assign the metric

\begin{equation}
g_{\mu\nu} \equiv \eta_{\mu\nu} = \text{diag} (1,1,\dots,1,-1,-1,\dots,-1)
\end{equation}

\noindent With the first $p$ entries equal to one, and the last $q$ entries equal to minus one. Note that this is not necessarily a Riemannian metric, since the signature can be negative. We have a few cases of interest for this metric

\begin{itemize}
\item $p=d$ , Riemannian.
\item $p = d-1$, $q=1$, Lorentz.
\item $q > 1$, e.g., $q=2$, AdS-CFT correspondence.
\end{itemize}

\noindent A conformal transformation leaves the metric invariant up to a scale factor. Consider a smooth change of coordinates

\begin{equation}
x \rightarrow x' = x' (x) \text{ , with } x = (x^1, x^2, \dots, x^p, x^{p+1}, \dots, x^{p+q})
\end{equation}

\noindent Such that for the metric, as a type-$(2,0)$ tensor,

\begin{equation}
g_{\mu\nu} (x) \rightarrow g'_{\mu\nu} (x') = \frac{\partial x^\alpha}{\partial x'^\mu} \frac{\partial x^\beta}{\partial x'^\nu} g_{\alpha \beta} (x) \equiv \Omega (x) g_{\mu\nu} (x).
\end{equation}

\noindent Where $\Omega(x) > 0$ is the (local) scale factor. Note that if the scale factor is zero, then we have a singularity, which we will discuss later. Such a transformation is called \textit{conformal}, and these transformations preserve angles

\begin{equation}
\angle \theta = \frac{g_{\mu\nu} u^\mu v^\nu}{\sqrt{(g_{\mu\nu} u^\mu v^\nu)^2}}.
\end{equation}

\noindent The \textit{conformal group} of a manifold M is denoted by $\text{Conf}(M)$, and is the connected component of the group of all conformal transformations of $M$ containing the identity, in a compact, open topology. \\

\noindent So, in a quantum conformal field theory, we are looking for a Hilbert space $\mathcal{H}$ and a projective unitary representation of the group $G$ for \textit{local} QFTs

\begin{equation}
G \rightarrow \pi (G).
\end{equation}

\noindent This is unexpectedly difficult, and makes for a very rich field of study, since there is a tension between knowing the unitary representations of symmetries and demanding that the representation is locally implementable. \\

\noindent To classify the conformal group on our chosen manifold $G = \text{Conf} (\mathbb{R}^{p,q})$, consider an infinitesimal conformal transformation on the spacetime coordinates

\begin{equation}
x^\mu \rightarrow x'^\mu = x^\mu +  \epsilon^\mu (x)
\end{equation}

\noindent Which acts on the metric, placing constraints on $\epsilon$, as (\textbf{Exercise})

\begin{equation}
g_{\mu\nu} \rightarrow g'_{\mu\nu} = g_{\mu\nu} + (\partial_\mu \epsilon_\nu + \partial_\nu \epsilon_\mu) + \mathcal{O} (\epsilon^2).
\end{equation}

\noindent To satisfy the condition $g'_{\mu\nu} (x') = \Omega(x) g_{\mu\nu} (x)$, we must have that the second term be diagonal, proportional to $\eta_{\mu\nu}$

\begin{equation}
(\partial_\mu \epsilon_\nu + \partial_\nu \epsilon_\mu) \propto \eta_{\mu\nu}.
\end{equation}

\noindent Calculate the proportionality factor by tracing both sides with $\eta_{\mu\nu}$ to get

\begin{equation}
\partial_\mu \epsilon_\nu + \partial_\nu \epsilon_\mu = \frac{2}{d} (\partial \cdot \epsilon) \eta_{\mu\nu}.
\end{equation}

\noindent Comparing this with the metric transformation law, we get that the scale factor $\Omega(x)$ is 

\begin{equation}
\Omega(x) = 1+\frac{2}{d} (\partial \cdot \epsilon).
\end{equation}

\noindent From equality of mixed partial derivatives (to third order), it follows that (\textbf{Exercise})

%\input{chapters/lec1.tex}

%\clearpage

\end{document}